---
title: "format IDR data for omop2obo"
author: "Dominick J. Lemas"
date: "2023-05-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(readr)
library(dplyr)

# input files 
# UFRC
# /blue/djlemas/share/data/Benchmark/OMOP/data_release/v2.1/clinical_data/

# shardrive
# V:\FACULTY\DJLEMAS\EHR_Data\processed\OMOP

# PC
data_path="V:/FACULTY/DJLEMAS/EHR_Data/processed/OMOP/"
data_file="condition_occurrence_head.csv"
data_file_path=paste0(data_path,data_file)

# Import Files
idr_condition <- read_csv(data_file_path, show_col_types = FALSE)

``

```{r cars}

idr_final = idr_condition %>%
  rename(CONCEPT_ID = condition_concept_id,
         CONCEPT_SOURCE_CODE = condition_type_concept_id,
         # CONCEPT_LABEL =
         # CONCEPT_SOURCE_LABEL
         # CONCEPT_VOCAB
         # CONCEPT_VOCAB_VERSION
         # CONCEPT_SYNONYM
         # ANCESTOR_CONCEPT_ID
         # ANCESTOR_SOURCE_CODE
         # ANCESTOR_LABEL
         # ANCESTOR_VOCAB
         # ANCESTOR_VOCAB_VERSION
         )

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
